Compare output pre and post adding strata

### 2024-08-05 Rmd/compare_output_pre_and_post_adding_strata.Rmd
update input file. results are the same as previous.

out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_7_30_24.RDS")

>>>>

# out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_7_30_24.RDS")
out2 = readRDS("C:/Users/bstacy2/OneDrive - UW/UW Postdoc/GitHub Repos/baseISS_data/outputs/ISS_1000iters_output_8_2_24.RDS")
